---
title: "Data Filtering: Exercise"
author: "Bert"
date: "18 März 2019"
output: 
  html_document:
    toc: true
    toc_float: true
    code_folding: show
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T, warning = F, message = F)
```

```{r}
library(dplyr)
library(babynames)
```

In this exercise you will work extensively on dplyr filtering and selection.

# Data Preparation

We will work with dataset "babynames" from the package with the same name.

```{r}
data("babynames")
babynames %>% 
  glimpse
summary(babynames)
```

# Filtering

1. Filter for year 2015.
```{r}
babynames_filt <- babynames %>%
  filter(year == 2015)
babynames_filt
```


2. Filter for all names that have a capital letter "B". Help: take a look at "str_detect()".
```{r}
library(stringr)
babynames_filt <- babynames %>%
  filter(str_detect(name, 'B'))
babynames_filt
```


3. Filter for male names.
```{r}
babynames_filt <- babynames %>%
  filter(sex == 'M') %>%
  select(name)
babynames_filt
```


4. Take only names into account which have more than 100 observations.
```{r}
babynames_filt <- babynames %>%
  filter(n > 100) %>%
  select(name)
babynames_filt
```


5. Show the Top 10 in decreasing order.
```{r}
babynames_filt <- babynames %>%
  arrange(desc(n)) %>%
  top_n(10)
babynames_filt
```


6. Keep only the columns "name" and "prop"

```{r}
babynames_filt <- babynames %>%
  select(name, prop)
babynames_filt
```

7. All in one
```{r}
babynames_filt <- babynames %>%
  filter(year == 2015)  %>%
  filter(str_detect(name, 'B')) %>%
  filter(n > 100) %>%
  arrange(desc(n)) %>%
  top_n(10) %>%
  select(name, prop)
babynames_filt
```

