---
title: "DataAgregation"
author: "Hendrilalaina"
date: "2025-03-17"
output: 
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    code_folding: show
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyr)
library(dplyr)
```


# Data Preparation
```{r}
data("population")
population
```

We use the dataset "population", which shows the population for countries and the period.
Data is stored in a tidy format.

```{r}
population %>%
  head()
```
# Population in Madagascar

```{r}
population %>%
  filter(country == 'Madagascar')
```


# Data Agregation
We want to calculate the min, max and increase  of population for each country.
At first, the data is grouped for the category that should be used for grouping. Then in the **summarise()** function, the logic is described.

```{r}
population %>%
  group_by(country) %>%
  summarise(min = min(population), max = max(population), increase = max - min, inc_percent = (max-min)/min*100)
```

