---
title: "R Markdown"
author: "Hendrilalaina"
date: "2025-03-17"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    code_folding: show
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Import

## CSV

This is the import of "Affairs.csv"

```{r}
library(readr)
affairs_csv <- read_csv(file = "./../RUltimateMaterial-main/data/Affairs.csv")
View(affairs_csv)
```

## Excel

This is the import of "Affaires.xlsx"

```{r}
library(readxl)
affairs_xlsx <- read_excel("./../RUltimateMaterial-main/data/Affairs.xlsx")
View(affairs_xlsx)
```

## JSON
JSON is a JavaScript Object Notation
```{r}
library(jsonlite)
affairs_json <- read_json(path = "./../RUltimateMaterial-main/data/Affairs.JSON", simplifyVector = T)
View(affairs_json)
```

## SPSS

SPSS is a statistical program with its own file format.

```{r}
library(foreign)
affairs_spss <- read.table("./../RUltimateMaterial-main/data/Affairs.sps")
View(affairs_spss)
```

## RDA

RDA is a native R format, which provides compression. RDA saves the object names and can store more than just one object.

```{r}
load(file = "./../RUltimateMaterial-main/data/Affairs.RDA")
```

## RDS

RDS is the new native R format. RDS does not store the object name and can only contain one object. It has a slightly better compression rate compared to RDA.

```{r}
affairs_rds <- readRDS("./../RUltimateMaterial-main/data/Affairs.RDS")
View(affairs_rds)
```

# Export

## CSV
Export of "affairs_csv"
```{r}
write.csv(x = affairs_csv, file = "./export/Affairs.csv")
```

## JSON
Export of "affairs_json"
```{r}
write_json(x = affairs_json, path = "./export/Affairs.json")
```

## SPSS
Export of "affairs_spss"
```{r}
write.foreign(affairs_spss, datafile = "./../RUltimateMaterial-main/data/Affairs.sps", codefile = "./export/Affairs.code", package = "SPSS")
```

## RDA and RDS
RDA and RDS are native R formats, which store data compressed.
```{r}
save(affairs_csv, file = "./export/Affairs.RDA")
saveRDS(affairs_csv, file = "./export/Affairs.RDS")
```


